API design for machine learning software: experiences from the scikit-learn project

### 2013-06-23 paper.tex
conclusion; mention nolearn
Fixes #19.

\textcolor{red}{TODO: include some overall conclusions (e.g., reasons of the success sklearn)}

>>>>

We have discussed the scikit-learn API
and the way it maps machine learning concepts and tasks
onto objects and operations in the Python programming language.
We motivated choices and compromises made in its design.
We argue that the API is powerful, usable and extensible,
as witnessed by the appearance of third-party packages
that follow the scikit-learn conventions and tie into the toolkit.\footnote{
  E.g.\ nolearn, \url{http://pythonhosted.org/nolearn};
  this mention does not imply endorsement of this package.}
While part of the scikit-learn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.
